### 2016-03-04 Projects/DelCo_2014_2015/Reports/FDS_Validation_Report/TeX_Files/FDS_Exp_Description_Report.tex
Minor edits to format of FDS exp report

\headerB{
Overview of Fire Model Validation Experiments in Residential Scale Structures \\
}

@@

@@

\begin{figure}[!ht]
	\includegraphics[width=5.25in]{../../Hose_Stream_Report/Figures/Pictures/east_structure}
	\\~\\
	\includegraphics[width=5.25in]{../../Hose_Stream_Report/Figures/Pictures/west_structure}
	\caption[North side of the east and West Structures.]{North side of the east (top) and west (bottom) test structures.}
	\label{fig:struct_pics}
\end{figure}

>>>>

\headerB{
Propane Gas Fire Experiments in Residential Scale Structures \\
}

@@

% [Brief Introduction of FRD at NIST, ventilation, etc.]

@@

\begin{figure}[!ht]
	\includegraphics[width=5.25in]{../../Hose_Stream_Report/Figures/Pictures/east_structure}
	\\~\\
	\includegraphics[width=5.25in]{../../Hose_Stream_Report/Figures/Pictures/west_structure}
	\caption[North side of the East and West Structures.]{North side of the East (top) and West (bottom) test structures.}
	\label{fig:struct_pics}
\end{figure}
